---
title: "Lab 3 Part 1 Binary Logistic Regression"
author: "Vanessa Rathbone"
date: "1/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(jtools)
```

```{r}
penguins %>% 
  select(species, bill_length_mm:sex) %>% 
  ggpairs(aes(color = species))

```

Create a subset with only Adelle and Chinstrap penguins.
```{r}
adelle_chinstrap <- penguins %>% 
  filter(species %in% c("Adelie", "Chinstrap")) %>% 
  mutate(species = fct_drop(species)) #drop observations for any factor that doesn't have any obervations, here Gentoo
```

Let's dataviz these two species
```{r}
ggplot(data = adelle_chinstrap, aes(x = body_mass_g, y = flipper_length_mm)) +
  geom_point(aes(color = sex)) +
  facet_wrap(~species)
```

Binary Logistic Regression

- Body Mass
- Flipper Length
- Penguin Sex

```{r}
adelle_chinstrap_blr <- glm(species ~ body_mass_g + flipper_length_mm + sex, data = adelle_chinstrap,
                         family = "binomial")
```

Take a look at the outcomes
```{r}
adelle_chinstrap_blr

summary(adelle_chinstrap_blr)

```

```{r}
ggplot(adelle_chinstrap, aes(x = species, y = flipper_length_mm)) +
  geom_jitter(aes(color = sex))
```

What are the actual probabilities of being a Chinstrap for each of the existing observations in our adelle_chinstrap data frame? 
```{r}
blr_fitted <- adelle_chinstrap_blr %>% 
  broom::augment(type.predict = "response")
#check "fitted" value in the data frame, this is the probability of being a chinstrap

```

Plotting fitted probabilities
```{r}
ggplot(blr_fitted, aes(x = flipper_length_mm, y = .fitted)) +
  geom_point(aes(color = sex, pch = species)) +
  geom_smooth(aes(color = sex), se = FALSE) +
  labs(x = "Flipper length (mm)",
       y = "Probability of outcome Chinstrap") 

```

Plot model based on different variables using effect_plot(). Good for quick looks at one variables effect on probability. 
```{r}
effect_plot(adelle_chinstrap_blr,
            pred = flipper_length_mm, 
            y.label = "Probability of Chinstrap",
            interval = TRUE)

effect_plot(adelle_chinstrap_blr,
            pred = body_mass_g, 
            y.label = "Probability of Chinstrap",
            interval = TRUE)
```

What is the probability that a female penguin eighing 3410 g with a flipper length of 192mm is a Chinstrap? 
```{r}
ex_1 <- predict(adelle_chinstrap_blr, 
                data.frame(sex = "female",
                           body_mass_g = 3410,
                           flipper_length_mm = 192),
                type = "response")

ex_1

#given these values there is a 0.40 or 40% chance that this penguin is a Chinstrap.
```

